\documentclass[12pt,a4paper]{article}

% Use custom style package
\usepackage{mystyle}

% Standard packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

\title{Comprehensive Multi-File LaTeX Test}
\author{Test Author\\
        Department of Computer Science\\
        Test University}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This document demonstrates a complete multi-file LaTeX compilation setup including a custom style file, bibliography, and multiple subsection files. It tests cross-references, citations, custom commands, and modular document structure.
\end{abstract}

\tableofcontents
\newpage

\section{Introduction}
This is the main document that orchestrates multiple files. As noted by \cite{knuth1984}, \TeX{} is a powerful typesetting system. We also reference \cite{lamport1994} for \LaTeX{} documentation.

% Include introduction subsection
\input{intro}

\section{Technical Content}
In this section, we demonstrate mathematical equations and custom styling.

% Include technical content
\input{technical}

\section{Results and Analysis}
Here we present findings with cross-references.

% Include results subsection
\input{results}

\section{Advanced Features}

\subsection{Custom Commands Demo}
Using our custom style package:
\begin{itemize}
    \item \important{Important text} - highlighted text
    \item \keyword{keyword} - styled keyword
    \item \customemph{emphasized text} - custom emphasis
\end{itemize}

\subsection{Custom Environment Demo}
\begin{notebox}
This is a custom note box defined in our mystyle.sty package. It demonstrates that custom environments work correctly in multi-file compilation.
\end{notebox}

\subsection{Cross-References}
We can reference equations like Equation~\ref{eq:einstein} and Equation~\ref{eq:quadratic} from included files. We can also reference sections like Section~\ref{sec:methodology}.

\section{Conclusion}
This document successfully demonstrates multi-file compilation with:
\begin{enumerate}
    \item Custom style package (mystyle.sty)
    \item Bibliography file (references.bib)
    \item Multiple subsection files in sections/ directory
    \item Cross-references between files
    \item Citations from BibTeX
\end{enumerate}

For more details on typesetting, see \cite{knuth1984} and \cite{lamport1994}. The recent work by \cite{goossens1994} also provides excellent examples.

\bibliographystyle{plain}
\bibliography{references}

\end{document}

